\documentclass[10pt]{beamer}
\usepackage{ragged2e} % \justifying
\usepackage[export]{adjustbox} % left and right in images
\usepackage{subcaption} % subfigure
\usepackage[none]{hyphenat} % Avoids to go out of margin
\usetheme{metropolis}           % Use metropolis theme
\title{Planning and Executing Humanoid Gaits\\in a World of Stairs}
\subtitle{Michele Cipriano}
%\date{\today}
\date{January 21, 2020}
%\author{Michele Cipriano}
\author{
  \textbf{Thesis Advisor:} Prof. Giuseppe Oriolo
}
\institute{Master Degree in Artificial Intelligence and Robotics\\
  Department of Computer, Control and Management
  Engineering\\Sapienza University of Rome}

% Fontsize of figure smaller than normalsize:
\setbeamerfont{caption}{size=\scriptsize}

\begin{document}
\nocite{*}

\maketitle

\justifying

\begin{frame}{Introduction}
  Abstract. Humanoid Robot Locomotion Problem. Approach + Block Scheme.
\end{frame}

\begin{frame}{Variable Height CoM IS-MPC}
  3D Motion Plan. Variable Height CoM Motion Model. MPC Formulation
  (ZMP constraints, stability constraints, algorithm+BHuman).

  Experiments: Normal Staircase. Simple Staircase. Multiple Staircases
  (Up/Down).
\end{frame}

\begin{frame}{RRT-based Footstep Planning}
  Problem Formulation: R1, R2, R3. How the planner works (briefly). NAO's
  catalogue of primitives.

  Experiment: Obstacle Avoidance.
\end{frame}

\begin{frame}{Elevation Map Generation}
  \texttt{elevation\_mapping}, features, how it works (briefly).
  Settings: NAO + Xtion + \textit{World of Stairs}.

  Experiments: Generated Map + Stair Climbing in Unknown Environment.
\end{frame}

\begin{frame}[standout]
  Video
\end{frame}

\begin{frame}{Conclusion}
  Results. Future Works.
\end{frame}

\begin{frame}[standout]
    Q\&A
\end{frame}

\appendix

\begin{frame}{References}
  \bibliography{bibliography}
  \bibliographystyle{ieeetr}
\end{frame}

\end{document}

